\tool: Revisiting BadUSB with Type-C\\ \thanks{$^{*}$~The first three authors contributed equally to this work.} \thanks{\textsuperscript{\Letter}~Fengwei Zhang is the corresponding author.}

### 2021-03-27 WOOT/BadUSBC.tex
Authors

\title{\tool: Revisiting BadUSB with Type-C}

\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1}\orcidA{}, Yechang Wu\textsuperscript{1}, Shuqing Li\textsuperscript{1}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2}}
\IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\
		\textsuperscript{2}\textit{Research Institute of Trustworthy Autonomous Systems, Southern University of Science and Technology} \\
	\{11712009,11711918,lisq2017,11711809,11712021\}@mail.sustech.edu.cn,zhangfw@sustech.edu.cn\\
}
}

>>>>

\title{\tool: Revisiting BadUSB with Type-C\\
\thanks{$^{*}$~The first three authors contributed equally to this work.}
\thanks{\textsuperscript{\Letter}~Fengwei Zhang is the corresponding author.}}

\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1,*}\orcidA{}, Yechang Wu\textsuperscript{1,*}, Shuqing Li\textsuperscript{1,*}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2,\Letter}}
\IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\
		\textsuperscript{2}\textit{Research Institute of Trustworthy Autonomous Systems, Southern University of Science and Technology} \\
	\{11712009,11711918,lisq2017,11711809,11712021\}@mail.sustech.edu.cn,zhangfw@sustech.edu.cn\\
}
}
